\documentclass[a4paper,11pt]{article}

\usepackage[super]{nth}

\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=0.5in]{geometry}
\usepackage{hyperref}

\titleformat{\section}
{\vspace{-0.3em}\LARGE}
{}
{0em}
{\bfseries}[\titlerule]

\titleformat{\subsection}[runin]
{}
{$\bullet$}
{0.5em}
{\bfseries}

\titlespacing{\subsection}
{0em}
{0.25em}
{0em}

\hypersetup{
	colorlinks=true,
	linkcolor=black,
	urlcolor=black                        
}
\urlstyle{same}

\renewcommand{\maketitle}{
	\begin{center}
		{\Huge \bfseries \textrm{\theauthor}}
		
		+91-63939-60694
		$|$
		403, Vignaharta CHS, Kharghar, Navi Mumbai, 410210
		
		
		\underline{akshaydwivedi0606@gmail.com}
		$|$
		\underline{\href{https://www.linkedin.com/in/akshaydwivedi10}{LinkedIn}}
		$|$
		\underline{\href{https://github.com/akshaynaresh}{Github}} 
		$|$
		\underline{\href{https://leetcode.com/aksnaresh/}{Leetcode}}
		$|$
		\underline{\href{https://codeforces.com/profile/aksnaresh}{Codeforces}}
		$|$
		\underline{\href{https://www.codechef.com/users/aksnaresh}{Codechef}}
		$|$
		\underline{\href{https://atcoder.jp/users/aksnaresh}{Atcoder}}
	
	\end{center}
}

\begin{document}



	\title{R\'esum\'e}
	\author{Akshay Dwivedi}
	\maketitle
	\thispagestyle{empty}



	\section{Education}
	
	\subsection{Bachelor of Technology in Computer Science and Information Technology}
	
    \textsl{\\{\hspace{0.5em}}KIET Group of Institutions, Ghaziabad, Uttar Pradesh, IN \underline{GPA-7.5}}
	
	{\hspace{-1.5em}}\textsl{Graduation Year: 2024}
	
	
	\subsection{Senior Secondary Education}
	
	\textsl{\\Rani Laxmi Bai Memorial School, Lucknow, Uttar Pradesh, IN \underline{Percentage-87.20\%}}
	
	{\hspace{-1.5em}}\textsl{Completion Year: 2019}



    \vspace{-1.1em}



    \section{Experience}

	\subsection{JPMorgan Chase \& Co. \hspace{21em} July 2022 - Jan 2023 \newline}

    \textsl{Software Engineering Virtual Experience} \textsl{\textbf{\href{https://drive.google.com/file/d/1aMeVe3rh78F99NR0c_5v8wemFDOtLfcP/view?usp=share_link}{(Certificate)}}}

	\hspace{-1.5em}\textsl{- Developed financial applications using industry-standard technologies, resulting in a 20\% increase in efficiency and productivity.}

	\hspace{-1.5em}\textsl{- Analyzed and visualized data for the trading floor, providing actionable insights and contributing to a 15\% improvement in decision-making processes.}
	


	
	\vspace{-1.1em}
	


	\section{Projects}
	
	\subsection{Sorting Visualizer{\hspace{27.5em}}\underline{\textsl{\href{https://github.com/akshaynaresh/Sorting-Visualizer}{(Github Link)}}}}
	
    \textsl{\\- Demonstrates various sorting algorithms in real-time.}
	
	\hspace{-1.5em}\textsl{- Implemented popular sorting algorithms such as Bubble Sort, Merge Sort, and Quick Sort }

	\hspace{-1.5em}\textsl{- Demonstrated proficiency in algorithm implementation, GUI development, and data visualization.}
	
	\subsection{Portfolio Website{\hspace{27.8em}}\underline{\textsl{\href{https://github.com/akshaynaresh/portfolio-website}{(Github Link)}}}}
	
	\textsl{\\- Created a professional portfolio showcasing full-stack web development expertise, resulting in a 20\% increase in user engagement and 10\% higher conversion rate.}
	
	{\hspace{-1.5em}}\textsl{- Designed an engaging user interface with responsive design to showcase projects effectively.}

	{\hspace{-1.5em}}\textsl{- Interactive portfolio highlighting projects with captivating visuals and descriptions.}
	
    \subsection{Personal Information Manager{\textbf{ (Major Project)}}{\hspace{15em}}\underline{\textsl{\href{https://github.com/akshaynaresh/Personal-Information-Manager}{(Github Link)}}}}
	
	\textsl{\\- Developed a Web Browser extension that improved productivity by automating repetitive tasks, saving an average of 2 hours per day for users.}
	
	\hspace{-1.5em}\textsl{- Access any document in your browser with just a shortcut.}

	\hspace{-1.5em}\textsl{- Functionality that filters your browser history to show all the documents you need for work in one place.}

	\hspace{-1.5em}\textsl{- Integration with GPT-4 to access the limitless power of AI for automating tedious tasks}




	\vspace{-1.1em}
	


	\section{Achievements \& Awards}
	
	\subsection{}\hspace{0.5em}\textbf{CodeForces Max. Rating: 1051 (Newbie)}
	\subsection{}\hspace{0.5em}\textbf{CodeChef Max. Rating: 1620 (3 Star) }
    \subsection{}\hspace{0.5em}Secured \textbf{\nth{85}} rank in \textbf{Starters-54} on Codechef (September 28, 2022)
	% \subsection{}\hspace{0.5em}Qualified for Round-1 of \textbf{Meta Hacker Cup 2022}
	% \subsection{}\hspace{0.5em}Participated in Round E and F of \textbf{Google Kickstart 2022} securing 
	% \textbf{\nth{5080}} rank in Round-F among 9300 participants



	\vspace{-1.1em}
	


	\section{Extracurriculars}
	
    \subsection{}\hspace{0.5em}Midfielder @ FC KIET(College Football Team) \textbar{} Oct 2021 - May 2022  
	\subsection{}\hspace{0.5em}Member @ KIET KODERS KORNER(Technical Club promoting Competitive Programming) 
	

    \vspace{-1.1em}



	\section{Technical Skills}
	\subsection{Languages}: JavaScript, Bash, Java, C, C++, Python, HTML, CSS, \LaTeX
	\subsection{Frameworks}: ReactJS, SQL
	\subsection{Developer Tools}: Arch Linux, i3gaps, tmux, Neovim, Git, VS Code, Sublime Text
	% \subsection{Other}: Data Structures and Algorithms, Competitive Programming
	




\end{document}
 
