\documentclass[11pt,a4paper]{article}
\usepackage[left=0.75in,right=0.75in,top=0.6in,bottom=0.6in]{geometry}
\usepackage{enumitem}

% Personal Information
\newcommand{\fullname}{Your Full Name}
\newcommand{\email}{your.email@example.com}
\newcommand{\phone}{(123) 456-7890}
\newcommand{\linkedin}{linkedin.com/in/yourprofile}
\newcommand{\github}{github.com/yourusername}
\newcommand{\website}{yourwebsite.com}

% Section Styles
\newcommand{\ressection}[1]{\vspace{8pt}\large\textbf{#1}\vspace{4pt}\\}
\newcommand{\ressubsection}[3]{\textbf{#1} \hfill #2\\ \textit{#3}\\}

\begin{document}
% Header
\begin{center}
    \LARGE\textbf{\fullname}\\
    \vspace{4pt}
    \small\email{} $\vert$ \phone{} $\vert$ \linkedin{} $\vert$ \github{} $\vert$ \website{}
\end{center}

% Objective/Summary
\ressection{Objective}
I am a motivated computer science undergraduate seeking internships or job roles where I can apply my skills and contribute to meaningful projects. With a strong foundation in programming and problem-solving, I am eager to learn and grow in a professional environment.

% Education
\ressection{Education}
\textbf{Bachelor of Science in Computer Science} \hfill \textit{Expected graduation: Month, Year}\\
University Name \hfill City, State\\
Relevant coursework: Data Structures, Algorithms, Database Systems, etc.

% Technical Skills
\ressection{Technical Skills}
\begin{itemize}[leftmargin=*]
    \item Programming languages: Java, Python, C++
    \item Software development tools and frameworks: Git, Visual Studio, IntelliJ IDEA
    \item Web development technologies: HTML, CSS, JavaScript
    \item Databases: SQL, MySQL, MongoDB
    \item Operating systems: Windows, Linux, macOS
    \item Other relevant technical skills or technologies
\end{itemize}

% Projects
\ressection{Projects}
\ressubsection{Project Name 1}{Date}{Technologies Used: Java, MySQL}
Description of the project and your contributions or achievements.

\ressubsection{Project Name 2}{Date}{Technologies Used: Python, Django, HTML, CSS}
Description of the project and your contributions or achievements.

% Work Experience
\ressection{Work Experience}
\ressubsection{Company Name 1}{Date}{Your Job Title}
Description of your responsibilities and achievements in the role.

\ressubsection{Company Name 2}{Date}{Your Job Title}
Description of your responsibilities and achievements in the role.

% Leadership and Involvement
\ressection{Leadership and Involvement}
\ressubsection{Club/Organization Name 1}{Date}{Your Position}
Description of your involvement, projects completed, or contributions made.

\ressubsection{Club/Organization Name 2}{Date}{Your Position}
Description of your involvement, projects completed, or contributions made.

% Awards and Honors
\ressection{Awards and Honors}
\begin{itemize}[leftmargin=*]
    \item Academic or industry-related awards, scholarships, or honors received.
\end{itemize}

% Extracurricular Activities
\ressection{Extracurricular Activities}
\begin{itemize}[leftmargin=*]
    \item Non-technical activities or hobbies that showcase your well-roundedness and transferable skills.
\end{itemize}

% References
\ressection{References}
Available upon request.

\end{document}

